---
title: "fs_fuel_treatment"
author: "Katherine Siegel"
date: "August 23, 2023"
output: html_document
---

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load packages
library(tidyverse)
library(sf)
library(lubridate)
library(raster)
library(terra)
```

## Key notes and next steps
There are some points that burned in multiple wildfires, and I don't know which one is actually relevant. This means that some sample points currently have more than 1 row, but because of the way I extracted the data, the composite burn index values are the same for both rows (because I just extracted the top layer's burn index value). The multiple overlapping fires also means there are NAs in fire_samples that shouldn't actually be there -- when I merged the rasters, the code created NA values in the unburned rectangles around the fires.

Next steps: figure out which fires actually matter for the control and treated points, re-do raster merge to make sure I'm including the correct fires for each sample point and not getting the NA pixels. Then extract the burn severity data to the dataset again.

## Get fires that overlapped with fuel treatments
```{r}
### Open fuel treatment database
ft <- st_read("E:/mtbs_rxfire_intersections/mtbs_rxfire_intersect_olddef.shp") 

### how many unique fires are there in ft?
length(unique(ft$Event_ID)) ## 72

### subset all fires to ft
mtbs <- st_read("E:/fire_sev_rdd/mtbs/mtbs_perims_DD.shp") %>%
  filter(., Event_ID %in% ft$Event_ID) %>%
  st_transform(crs = 5070)

### check for types of fires included here
table(mtbs$Incid_Type)
## 11 prescribed
### 3 unknown
### 57 wildfire
### 1 wildland fire use

### leaving all fire types in for now, but seems like we should restrict moving forward.
```
### export fire perimeters for CBI analysis
- Fire_ID
- Fire_Year
- Start_Day (start day of fire season in Julian days)
- End_Day (end day of fire season in Julian days)
```{r}
### add date cols
mtbs <- mtbs %>%
  tidyr::separate(Ig_Date, c('year', 'month', 'day'), 
                  sep = "-",
                  remove = FALSE) %>%
  mutate_at(c('year', 'month', 'day'), as.numeric)

### reduce cols
mtbs_gee <- mtbs %>%
  dplyr::select(Event_ID,
                Incid_Type,
                Ig_Date, 
                date = day,
                month, 
                year,
                geometry)

# ### Group by state and see earliest date of ignition
# ig_earlies <- recent_fires_gee
# ig_earlies$geometry <- NULL
# ig_earlies <- ig_earlies %>%
#   group_by(year) %>%
#   summarise(earliest_ig_month = min(month),
#             latest_ig_month = max(month))

### Fire seasons
#### In Parks et al. 2019, they use the following seasons:
#### AZ and NM: April 1-June 30 (julian 91-181)
#### CA, ID, MT, OR, UT, WA, WY: June 1-Sept 15 (julian 152-258)
#### use these
# other_julian <- c("CA", "CO", "ID",
#                   "MT", "NV", "OR",
#                   "SD", "TX",
#                   "UT", "WA", "WY")

### use julian fire season dates for CA, ID, MT, OR, UT, WA, WY

### assign julian start and end date based on state dates from Parks et al. 2019
mtbs_gee <- mtbs_gee %>%
  mutate(Start_Day = 152,
         End_Day = 258)

### Select columns for GEE
mtbs_gee <- mtbs_gee %>%
  dplyr::select(Fire_ID = Event_ID,
                Fire_Year = year,
                Start_Day,
                End_Day,
                Incid_Type,
                geometry)

### Make sure date columns don't get read in with decimals
mtbs_gee$Fire_Year <- as.character(mtbs_gee$Fire_Year, 0)
mtbs_gee$Start_Day <- as.character(mtbs_gee$Start_Day, 0)
mtbs_gee$End_Day <- as.character(mtbs_gee$End_Day, 0)

### Write out shp for gee
st_write(mtbs_gee,
         "C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/co_mtbs_gee.shp")
```

## CBI for control points
```{r}
### all fires
mtbs <- st_read("E:/fire_sev_rdd/mtbs/mtbs_perims_DD.shp") %>%
  st_transform(crs = 5070)

### open data
sample_pts <- st_read("C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/USDA_sample_points/samplepoints500_co_fs.shp") %>%
  st_transform(crs = 5070) %>%
  
  ### add unique identification column
  mutate(uid = 1:nrow(sample_pts))

### by state
mtbs <- mtbs %>%
  mutate(state = stringr::str_extract(Event_ID, "^.{2}"))

### filter to CO and surrounding states
mtbs_co <- mtbs %>%
  filter(state %in% c("CO", "UT", "AZ", "NM", 
                      "WY", "OK", "KS", "NE"))

### reduce cols
mtbs_co <- mtbs_co %>%
  dplyr::select(Event_ID, Incid_Type, geometry)

### intersect with points
sample_fires <- st_intersection(sample_pts,
                                mtbs_co)

### new fire perimeters that I need
control_mtbs <- mtbs_co %>%
  
  ### fires in the sample
  filter(Event_ID %in% sample_fires$Event_ID) %>%
  
  ### drop fires I already did
  filter(!Event_ID %in% ft$Event_ID)

```
#### points in multiple fires?
```{r}
check <- sample_fires
st_geometry(check) <- NULL
check <- check %>%
  group_by(uid) %>%
  summarise(n_fires = n())
check <- check %>%
  filter(n_fires > 1)

### what do these look like?
check_fires <- sample_fires %>%
  filter(uid %in% check$uid)

### what do they look like in Anna's sample pts?
check_pts <- sample_pts %>%
  filter(uid %in% check$uid)
```

### export fire perimeters for CBI analysis
- Fire_ID
- Fire_Year
- Start_Day (start day of fire season in Julian days)
- End_Day (end day of fire season in Julian days)
```{r}
### get full data for mtbs from control pts
mtbs_control <- mtbs %>%
  filter(Event_ID %in% control_mtbs$Event_ID)
  
### add date cols
mtbs_control <- mtbs_control %>%
  tidyr::separate(Ig_Date, c('year', 'month', 'day'), 
                  sep = "-",
                  remove = FALSE) %>%
  mutate_at(c('year', 'month', 'day'), as.numeric)

### reduce cols
mtbs_control <- mtbs_control %>%
  dplyr::select(Event_ID,
                Incid_Type,
                Ig_Date, 
                date = day,
                month, 
                year,
                geometry)

### add state
mtbs_control <- mtbs_control %>%
  mutate(state = stringr::str_extract(Event_ID, "^.{2}"))

### Fire seasons
#### In Parks et al. 2019, they use the following seasons:
#### AZ and NM: April 1-June 30 (julian 91-181)
#### CA, ID, MT, OR, UT, WA, WY: June 1-Sept 15 (julian 152-258)
#### use these
# other_julian <- c("CA", "CO", "ID",
#                   "MT", "NV", "OR",
#                   "SD", "TX",
#                   "UT", "WA", "WY")

### use julian fire season dates for CA, ID, MT, OR, UT, WA, WY

### assign julian start and end date based on state dates from Parks et al. 2019
mtbs_control <- mtbs_control %>%
  mutate(Start_Day = ifelse(state == "NM", 91, 152),
         End_Day = ifelse(state == "NM", 181, 258))

### Select columns for GEE
mtbs_control <- mtbs_control %>%
  dplyr::select(Fire_ID = Event_ID,
                Fire_Year = year,
                Start_Day,
                End_Day,
                Incid_Type,
                geometry)

### Make sure date columns don't get read in with decimals
mtbs_control$Fire_Year <- as.character(mtbs_control$Fire_Year, 0)
mtbs_control$Start_Day <- as.character(mtbs_control$Start_Day, 0)
mtbs_control$End_Day <- as.character(mtbs_control$End_Day, 0)

### Write out shp for gee
st_write(mtbs_control,
         "C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/co_mtbs_control_gee.shp")
```

## Add CBI data
### extract CBI to points within MTBS perimeters (sample_fires)
```{r}
### list CBI files
cbi_list <- list.files(path = "C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/cbi_usda_gee",
                       pattern = "*\\.tif$",
                       full.names = TRUE)

### open files
cbi_rasts <- lapply(cbi_list, terra::rast)

### combine rasters into SpatRasterCollection
cbi_src <- sprc(cbi_rasts)

### merge
cbi_merge <- merge(cbi_src)

### reproject
cbi_merge <- terra::project(cbi_merge,
                            "epsg:5070",
                            method = "bilinear")

# ### write out for visual check
# terra::writeRaster(cbi_merge, 
#                    "C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/co_cbi.tif",
#                    filetype = "GTiff",
#                    overwrite = TRUE)
# st_write(sample_fires, "C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/co_sample_pts.shp")


### extract cbi to sample points
sample_cbi <- terra::extract(cbi_merge, sample_fires)

### combine with sample_fires sf df
sample_fires <- sample_fires %>%
  mutate(cbi_severity = sample_cbi[, -1])

### add column to indicate whether point is within an mtbs perimeter
sample_fires <- sample_fires %>%
  mutate(burned_mtbs = ifelse(is.na(cbi_severity), 0, 1))
```

### combine with the rest of the control data
```{r}
### get unburned pts
sample_control <- sample_pts %>%
  filter(!uid %in% sample_fires$uid)

### add relevant columns
sample_control <- sample_control %>%
  mutate(Event_ID = NA,
         Incid_Type = NA,
         cbi_severity = NA,
         burned_mtbs = 0)

### reorder cols
sample_control <- sample_control %>%
  dplyr::select(uid, lon, lat, 
                b1_Severit, b2_Severit, b3_Severit, 
                treated, WUI, aspect, slope, DEM, nlcd, 
                b1_Sever_1, b2_Sever_1, b3_Sever_1, 
                treated_1, WUI_1, aspect_1, slope_1, 
                DEM_1, nlcd_1, rxburn_bin, CO_nlcd, 
                aspect_co, slope_co, dem_CO, 
                Event_ID, Incid_Type, cbi_severity, burned_mtbs,
                geometry)
sample_fires <- sample_fires %>%
  dplyr::select(uid, lon, lat, 
                b1_Severit, b2_Severit, b3_Severit, 
                treated, WUI, aspect, slope, DEM, nlcd, 
                b1_Sever_1, b2_Sever_1, b3_Sever_1, 
                treated_1, WUI_1, aspect_1, slope_1, 
                DEM_1, nlcd_1, rxburn_bin, CO_nlcd, 
                aspect_co, slope_co, dem_CO, 
                Event_ID, Incid_Type, cbi_severity, burned_mtbs,
                geometry)

### combine
all_pts <- rbind(sample_control, 
                 sample_fires)

### write out
st_write(all_pts,
         "C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/all_sample_pts.shp")
```

