---
title: "fs_fuel_treatment"
author: "Katherine Siegel"
date: "August 26, 2022"
output: html_document
---

## Description
Code from August-September 2022 to determine which fuel treatments in CO subsequently burned in wildfires.

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load packages
library(tidyverse)
library(sf)
library(lubridate)
library(raster)
```

## Prep fuel treatment dataset for GEE
```{r}
### Open fuel treatment database
ft <- st_read("C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/S_USA.Activity_HazFuelTrt_PL.shp") 

### Subset to states around CO
ft <- ft %>%
  filter(STATE_ABBR %in% c("UT", "CO",
                           "WY", "NE",
                           "KS", "OK"))

### Reproject fuel treatments
ft <- ft %>%
  st_transform(crs = 6350)

### Open Colorado boundary
co_bound <- raster::getData(name = "GADM",
                            country = 'USA',
                            level = 1) %>%
  st_as_sf() %>%
  filter(NAME_1 == "Colorado")

### Reproject CO
co_bound <- co_bound %>%
  st_transform(crs = 6350) %>%
  dplyr::select(NAME_1, geometry)

# ### Write out CO shp
# st_write(co_bound,
#          "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_boundary.shp")

### Intersect treatment boundaries with CO
co_ft <- st_intersection(ft, co_bound)

### See which treatment types are present
unique(co_ft$METHOD)

### Filter out chemical and grazing
co_ft <- co_ft %>%
  filter(!METHOD %in% c("Animal",
                        "Chemical"))

### Take out treatments where completed date = NA
co_ft <- co_ft %>%
  drop_na(DATE_COMPL)

### Write out
st_write(co_ft,
         "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments.shp")

### Get range of treatment sizes
range(co_ft$GIS_ACRES)


co_ft %>%
  ggplot(aes(x = log(GIS_ACRES))) + 
  geom_histogram(color = "black",
                 fill = "white",
                 binwidth = 0.5) +
  # geom_vline(aes(xintercept = mean(GIS_ACRES)),
  #           color = "blue", 
  #           linetype = "dashed",
  #           size = 1) +
  NULL

```

### GEE -- don't run this here!
Use GEE to get forested area in each treatment footprint, based on NLCD 2019 release
```{python}
// Code to calculate # of forest pixels within each 
// fuels treatment in Colorado

// Data sources: NLCD (all years in Earth Engine),
//               fuel treatment perimeters

// Check that fuel treatment data read in correctly
//Map.addLayer(ft, {}, "test")

// Subset NLCD to landcover band
var nl_lc = nlcd.select('landcover');

// Reclassify to forest = 100, not forest = 1 in all years
// 41, 42, 43 are the forest classes
var nl_lc_rc = nl_lc.map(function(image){
  return image.remap(
    [11, 12, 21, 22, 23, 24, 31, 41, 42, 43, 
    51, 52, 71, 72, 73, 74, 81, 82, 90, 95],
    [1, 1, 1, 1, 1, 1, 1, 100, 100, 100, 
    1, 1, 1, 1, 1, 1, 1, 1, 1, 1]);
});
//  return image.remap(forest_lc, 1, 0);
// print('All metadata', nl_lc_rc);     

// Make "sum" layer -- this layer adds land cover data from all years
var sum = nl_lc_rc.sum();
//print('All metadata', sum);
  
// Reclassify this raster layer to be ever-forested vs. never-forested
var forest_rc = ee.Image(1)
      .where(sum.gte(-1).and(sum.lte(95)), 0)
      .where(sum.gt(99).and(sum.lte(900)), 1);
//print('All metadata', forest_rc);
Map.addLayer(forest_rc, {min:0, max: 1}, "land cover")

// Make dummy raster
var dummy_raster = ee.Image(1)
      .where(sum.gte(-1).and(sum.lte(95)), 1)
      .where(sum.gt(99).and(sum.lte(900)), 1);

// Sum pixels that are forest
var reduced_original = forest_rc.reduceRegions({
  collection: ft,
  reducer: ee.Reducer.sum(), 
  scale: 30
})

// Rename 'sum' property so it doesn't get overridden
var reduced_renamed = reduced_original.map(function(feat){
  return ee.Feature(feat.geometry(), { 
    unique_id: feat.get('unique_id'),
    sum_forest: feat.get('sum'),
  })
});

// Sum all pixels
var reduced = dummy_raster.reduceRegions({
  collection: reduced_renamed,
  reducer: ee.Reducer.sum(), 
  scale: 30
});

// Function to generate pixel counts
var PixCountFunction = function(feature) {
  var totalPixels = feature.get('sum')
  var forested_area = feature.get('sum_forest')
  var nonforested_area = ee.Number(totalPixels).subtract(forested_area)
  var feature1 =  feature.set("pixels_total", totalPixels).set("pixels_forest", forested_area).set("pixels_nonforest", nonforested_area)
  return feature1
}

// Run function on data
var forestAreas = reduced.map(PixCountFunction);

// Export csv to drive
Export.table.toDrive({
  collection: forestAreas,
  description: 'forest_area_treatment',
  fileNamePrefix: 'forest_area_treatment',
  fileFormat: 'CSV',
  selectors: ["unique_id", "pixels_forest", "pixels_nonforest"]
});


```


### GEE output
```{r}
### Open output csv
ft_area <- read_csv("C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/forest_area_treatment_CO.csv")

### Add column for total pixels
ft_area <- ft_area %>%
  mutate(total_pix = pixels_forest + pixels_nonforest,
         proportion_forest = pixels_forest/total_pix,
         proportion_nforest = pixels_nonforest/total_pix)

### Open treatment shp to get areas
ft_shp <- st_read("C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments.shp")

### Calculate areas (crs = 6350)
ft_shp <- ft_shp %>%
  mutate(treatment_area = st_area(ft_shp),
         treatment_area_ha = as.numeric(treatment_area)/10000)

### Merge with pixel counts
ft_shp <- merge(ft_shp, ft_area,
                by = "unique_id")

### Calculate forest area and nonforest area
ft_shp <- ft_shp %>%
  mutate(forest_area_ha = treatment_area_ha * proportion_forest,
         nonforest_area_ha = treatment_area_ha * proportion_nforest)

### Save as shp 
st_write(ft_shp, 
         "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments_forestarea.shp")

### Save as csv
ft_shp_csv <- ft_shp
st_geometry(ft_shp_csv) <- NULL
write_csv(ft_shp_csv, 
          "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments_forestarea.csv")

### Visualize
hist <- ft_shp %>%
  ggplot(aes(x = proportion_forest)) + 
  geom_histogram(color = "blue",
                 fill = "white",
                 binwidth = 0.05) +
  xlab("Proportion of pixels forested") +
  ylab("Number of treatment footprints") +
  # geom_vline(aes(xintercept = mean(GIS_ACRES)),
  #           color = "blue", 
  #           linetype = "dashed",
  #           size = 1) +
  NULL
```

### Combine and subset treatments
```{r}
### Open treatment shp and csv
treat <- st_read("C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments_forestarea.shp")
treatment_csv <- read.csv("C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments_forestarea.csv")
treatment_csv$geometry <- NA

### Rename shp cols
fullnames <- colnames(treatment_csv)
colnames(treat) <- fullnames

### How many treatments are > 50% forested?
ft_50 <- treat %>%
  filter(proportion_forest > 0.5)

### How many treatments have at least 5 forested ha?
ft_5ha <- treat %>%
  filter(forest_area_ha >= 5)
### 6590 treatment records

### Some of these treatment records are different activities that took place at the same location at the same time (ex. thinning and biomass removal)

### Make unique identifier for treatment footprints
tr_footprint <- ft_5ha 
st_geometry(tr_footprint) <- NULL
tr_footprint <- tr_footprint %>%
  dplyr::select(SUID, ORG, ASU_NBR_UN, ASU_UOM,
                ADMIN_REGI, ADMIN_FORE, ADMIN_DIST,
                STATE_ABBR, OWNERSHIP_, PROC_REGIO,
                PROC_FORES, MGT_AREA_C, NBR_UNITS_,
                NBR_UNITS1, UOM, DATE_PLANN,
                DATE_AWARD, DATE_COMPL, FISCAL_YEA,
                FY_AWARDED, FISCAL_Y_1, FY_PLANNED,
                KEYPOINT, FUND_CODE, NEPA_DOC_N,
                ACCOMPLISH, ACCOMPLI_1,
                pixels_forest) %>%
  distinct() %>%
  mutate(footprint_id = row_number())

### Merge footprint ID into full dataset
ft_5ha_footprint <- merge(ft_5ha,
                          tr_footprint,
                          by = c("SUID", "ORG",
                                 "ASU_NBR_UN",
                                 "ASU_UOM",
                                 "ADMIN_REGI",
                                 "ADMIN_FORE", 
                                 "ADMIN_DIST",
                                 "STATE_ABBR",
                                 "OWNERSHIP_",
                                 "PROC_REGIO",
                                 "PROC_FORES",
                                 "MGT_AREA_C",
                                 "NBR_UNITS_",
                                 "NBR_UNITS1",
                                 "UOM", "DATE_PLANN",
                                 "DATE_AWARD", "DATE_COMPL",
                                 "FISCAL_YEA", "FY_AWARDED",
                                 "FISCAL_Y_1", "FY_PLANNED",
                                 "KEYPOINT", "FUND_CODE",
                                 "NEPA_DOC_N", "ACCOMPLISH",
                                 "ACCOMPLI_1",
                                 "pixels_forest"),
                          all = TRUE)

## Do these treatments have multiple methods?
mech_fire <- ft_5ha_footprint
st_geometry(mech_fire) <- NULL
```

## Group by TREATMENT_
```{r}
### Drop method_summ column
ft_5ha_footprint$method_summ <- NULL

## Do these treatments have multiple methods?
unique(ft_5ha_footprint$TREATMENT_)

### methods categorizing
TREATMENT_ <- unique(ft_5ha_footprint$TREATMENT_)
category_tr <- c("fire", "combined", "mechanical",
                 "mechanical", "mechanical", "mechanical",
                 "fire", "fire", "mechanical",
                 "mechanical", "grazing", "NA", "NA")
treat_cat <- cbind.data.frame(TREATMENT_,
                              category_tr)

### Add this in
ft_5ha_footprint <- merge(ft_5ha_footprint,
                          treat_cat,
                          by = "TREATMENT_")

### Look at grazing
grazing <- ft_5ha_footprint %>%
  filter(category_tr == "grazing")

### Drop grazing
ft_5ha_footprint <- ft_5ha_footprint %>%
  filter(!category_tr == "grazing")

### Do these treatments have multiple methods?
mech_fire <- ft_5ha_footprint
st_geometry(mech_fire) <- NULL

#### List methods in each footprint
unique_methods <- mech_fire %>%
  group_by(footprint_id) %>%
  summarise(all_methods = list(unique(category_tr)))

### Get footprint IDs for methods
fire_meth <- unique_methods %>% 
  filter(all_methods == "fire") %>%
  mutate(method_summ = "fire")
mech_meth <- unique_methods %>% 
  filter(all_methods == "mechanical") %>%
  mutate(method_summ = "mechanical")
combined_meth <- unique_methods %>% 
  filter(all_methods == "combined") %>%
  mutate(method_summ = "combined")
na_meth <- unique_methods %>% 
  filter(is.na(all_methods)) %>%
  mutate(method_summ = "NA")

### Combine
methods_summary <- rbind(fire_meth,
                         mech_meth,
                         combined_meth,
                         na_meth)
methods_summary$all_methods <- NULL

### Footprints with multiple methods
mult_meth <- mech_fire %>%
  filter(!footprint_id %in% methods_summary$footprint_id) %>%
  dplyr::select(footprint_id) %>%
  mutate(method_summ = "combined")

### rbind
all_methods <- rbind(mult_meth, methods_summary)
all_methods <- distinct(all_methods)

### Number of footprints per method
table(all_methods$method_summ)

### Bring into shp
ft_5ha_footprint <- merge(ft_5ha_footprint,
                          all_methods,
                          by = "footprint_id",
                          all = TRUE)

### Save as shp 
st_write(ft_5ha_footprint, 
         "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments_subset_for_analysis.shp")
```


### Summary for proposal
```{r}
### drop geom
proposal_dat <- ft_5ha_footprint
st_geometry(proposal_dat) <- NULL

### summarize treatments
proposal_treat <- proposal_dat %>%
  group_by(mthd_sm, 
           TREATMENT_) %>%
  summarise(num_occurs = n(),
            total_area_h = sum(proposal_dat$frst_r_))

proposal_treat$total_area_h <- round(proposal_treat$total_area_h, 2)
  
### write out csv
write_csv(proposal_treat,
          "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/treatment_summary.csv")

### simplify
proposal_treat$method_summ <- NULL
proposal_treat <- proposal_treat %>%
  group_by(TREATMENT_) %>%
  summarise(num_occurs = sum(num_occurs),
            total_area_h = sum(total_area_h))

### average treatment area per treatment
t_area <- proposal_dat %>%
  group_by(TREATMENT_) %>%
  summarise(avg_area_ha = mean(forest_area_ha))
t_area$avg_area_ha <- round(t_area$avg_area_ha)

```


## Forest Service land in CO
```{r}
### Open CO bounds
### give it same crs as PAD database
co_bound <- st_read("C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_boundary.shp") %>%
  st_transform(crs = 5070)

### Open PAD
w_pad <- st_read("E:/usgs_pad/pad_west_valid.shp")

### Subset PAD to CO USFS
co_pad <- w_pad %>%
  filter(State_Nm == "CO" &
           Own_Name == "USFS")

### st transform
co_pad <- co_pad %>%
  st_transform(crs = 6350)

### write out
st_write(co_pad,
         "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_usfs.shp")


### write out as 4269
co_pad <- co_pad %>% st_transform(crs = 4269)
co_bound <- co_bound %>% st_transform(crs = 4269)
st_write(co_pad,
         "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_usfs_4269.shp")
st_write(co_bound,
         "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_bound_4269.shp")

### open treatments
co_treat <- st_read("C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments_subset_for_analysis.shp") %>%
  st_transform(crs = 4269)
st_write(co_treat,
         "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treat_4269.shp")

```

## How many treatments subsequently burned?
```{r}
### Open treatments
co_treat <- st_read("C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments_subset_for_analysis.shp") %>%
  st_transform(crs = 5070)

### Open MTBS 
mtbs <- st_read("E:/fire_sev_rdd/mtbs/mtbs_perims_DD.shp") %>%
  st_transform(crs = 5070)

### Restrict MTBS to colorado
mtbs <- mtbs[grep(paste("CO"),
                  mtbs$Event_ID), ]

### Separate out year as column
mtbs <- mtbs %>%
  mutate(date = day(Ig_Date),
         month = month(Ig_Date),
         year = year(Ig_Date))

### Add date cols for treatments
co_treat <- co_treat %>%
  mutate(date_comp = day(DATE_CO),
         month_comp = month(DATE_CO),
         year_comp = year(DATE_CO))

### treatments completed range from 1997-2022

### drop MTBS fires before 1997
mtbs <- mtbs %>%
  filter(year > 1996)

### drop treatments that were completed after end of MTBS time series
co_treat <- co_treat %>%
  filter(year_comp < 2021)

### Loop to figure out which treatments burned after treatment
store_intersect_all <- list()

for (i in 1:length(unique(co_treat$uniqu_d))) {
  
  ### progress bar
  print(paste0("STEP ", i))
  
  ### get treatment i
  co_tr_temp <- co_treat[i, ]
  
  ### subset to fires that burned after
  mtbs_temp <- mtbs %>%
    filter(Ig_Date > co_tr_temp$DATE_CO)
  
  ### Intersect
  temp_intersect <- st_intersection(co_tr_temp, mtbs_temp)
  
  ### store intersections as a list
  store_intersect_all[[i]] <- list(temp_intersect, unique(co_treat$uniqu_d)[i])
  
}

### Now need code to see how many treatments actually burned
### See how many treatments burned
co_treat_burn <- co_treat[1, ]
co_treat_burn <- co_treat_burn %>%
  mutate(uniqu_d = "empty")

### drop geom
st_geometry(co_treat_burn) <- NULL

### drop cols
co_treat_burn <- co_treat_burn %>%
  dplyr::select(ftprnt_, uniqu_d)

### add cols for merge
co_treat_burn <- co_treat_burn %>%
  mutate(Event_ID = NA, 
         Incid_Name = NA,
         Incid_Type = NA, 
         Ig_Date = NA,
         date = NA, month = NA, year = NA)

for (i in 1:length(store_intersect_all)) {
# for (i in 1:10) { ## make sure it works on subset of data
  
  ### make df
  temp_data <- as.data.frame(store_intersect_all[[i]][[1]])
  
  ### drop geom
  temp_data$geometry <- NULL
  
  ### Subset columns
  temp_data <- temp_data %>%
    dplyr::select(ftprnt_, uniqu_d,
                  Event_ID, Incid_Name,
                  Incid_Type, Ig_Date,
                  date, month, year)
  
  if(nrow(temp_data) > 0) {
    
    ### rbind with co_treat_burn
    co_treat_burn <- rbind(co_treat_burn,
                           temp_data)
  } 
  
}

### drop the empty row
co_treat_burn <- co_treat_burn %>%
  filter(!uniqu_d == "empty")

### subset to wildfires
wild_treat <- co_treat_burn %>%
  filter(Incid_Type == "Wildfire")

### write this out
write_csv(wild_treat,
          "C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments_that_burned.csv")

### Counts
length(unique(wild_treat$ftprnt_)) ## 498
length(unique(wild_treat$uniqu_d)) ## 592

### Look more closely
co_treat_burned <- co_treat %>%
  filter(uniqu_d %in% wild_treat$uniqu_d)

### fire treatments
co_fire <- co_treat_burned %>%
  filter(mthd_sm == "fire")
```

### visual for toronto talk
```{r}
### treatments that subsequently burned
treat_burn <- co_treat %>%
  filter(ftprnt_ %in% co_treat_burned$ftprnt_)

### Beaver Creek treatments
beaver_creek <- wild_treat %>%
  filter(Incid_Name == "BEAVER CREEK")

### treatments that burned in beaver creek fire
bc_treat <- co_treat %>%
  filter(ftprnt_ %in% beaver_creek$ftprnt_)

### Get these treatments as sf
### Open treatments
co_treat <- st_read("C:/Users/Katherine Siegel/Documents/Dee Lab/USDA AFRI/co_treatments_subset_for_analysis.shp") %>%
  st_transform(crs = 5070) %>%
  filter(., ftprnt_ %in% beaver_creek$ftprnt_)

### beaver creek sf
bc_sf <- mtbs %>%
  filter(Event_ID == "CO4095810663420160619")

### as factor
co_treat$ftprnt_ <- as.factor(co_treat$ftprnt_)

### drop the footprints that are off to the west
co_treat <- co_treat %>%
  filter(!(ftprnt_ == "2265" | ftprnt_ == "2266"))

### visualize
ggplot() +
  geom_sf(data = bc_sf) +
  geom_sf(data = co_treat,
          aes(color = ftprnt_)) +
  coord_sf(crs = 5070) +
  # xlim(106.3, 106.7) +
  NULL

### open burn severity mosaic from MTBS
burn_sev <- raster("C:/Users/Katherine Siegel/Documents/Job search/Faculty apps/My materials/2022_2023 cycle/1_9_Toronto/composite_data/mtbs_CO_2016.tif")

# ### figure out its epsg code
# pj4 <- "+proj=aea +lat_0=23 +lon_0=-96 +lat_1=29.5 +lat_2=45.5 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs"
# epsg <- rgdal::showEPSG(pj4)

### reproject burn sev
burn_sev <- projectRaster(burn_sev,
                          crs = crs(bc_sf))

### reproject sfs to match raster
p4s_bs <- proj4string(burn_sev)
co_treat_rpj <- co_treat %>%
  st_transform(crs = proj4string(burn_sev))
bc_sf_rpj <- bc_sf %>%
  st_transform(crs = proj4string(burn_sev))

### write out
st_write(co_treat_rpj,
         "C:/Users/Katherine Siegel/Documents/Job search/Faculty apps/My materials/2022_2023 cycle/1_9_Toronto/composite_data/treatments.shp")
st_write(bc_sf_rpj,
         "C:/Users/Katherine Siegel/Documents/Job search/Faculty apps/My materials/2022_2023 cycle/1_9_Toronto/composite_data/fire_boundary.shp")
```


## OLD: group by CAT_NM
```{r}
#### List methods in each footprint
unique_methods <- mech_fire %>%
  group_by(footprint_id) %>%
  summarise(all_methods = list(unique(CAT_NM)))

### Get footprint IDs for methods
fire_meth <- unique_methods %>% 
  filter(all_methods == "Fire") %>%
  mutate(method_summ = "Fire")
wildfire_meth <- unique_methods %>% 
  filter(all_methods == "Wildfire Non-Treatment") %>%
  mutate(method_summ = "Wildfire Non-Treatment")
mech_meth <- unique_methods %>% 
  filter(all_methods == "Mechanical") %>%
  mutate(method_summ = "Mechanical")
other_meth <- unique_methods %>% 
  filter(all_methods == "Other") %>%
  mutate(method_summ = "Other")
na_meth <- unique_methods %>% 
  filter(is.na(all_methods)) %>%
  mutate(method_summ = "none")

### Combine
methods_summary <- rbind(fire_meth,
                         wildfire_meth,
                         mech_meth,
                         other_meth,
                         na_meth)
methods_summary$all_methods <- NULL
methods_summary <- methods_summary %>%
  dplyr::select(footprint_id, methods_summ)

### Footprints with multiple methods
mult_meth <- mech_fire %>%
  filter(!footprint_id %in% methods_summary$footprint_id) %>%
  dplyr::select(footprint_id) %>%
  mutate(method_summ = "fire and mechanical")

### rbind
all_methods <- rbind(mult_meth, methods_summary)
all_methods <- distinct(all_methods)

### Number of footprints per method
table(all_methods$method_summ)

### Bring into shp
ft_5ha_footprint <- merge(ft_5ha_footprint,
                          all_methods,
                          by = "footprint_id",
                          all = TRUE)
```
Treatments that covered at least 5 ha of forest: 6590. This includes 5650 unique "footprints" (multiple treatments could take place at the same time within a single footprint). Within these treatment footprints, 3532 received mechanical treatments, 2030 received prescribed fire, and 7 received both. Another 76 treatment footprints received wildfire non-treatment, 2 were classified as "none", and 3 as "other"


