---
title: "ft_overlaps_simple"
output: html_document
date: "2024-02-02"
---

## Description
Pick up from chunk labeled "Intersect with fires" in ft_overlaps.Rmd and try a simpler approach to getting fuel treatment history at each point

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load packages
library(tidyverse)
library(sf)
library(lubridate)
library(raster)
library(terra)
# library(viridis)
# library(scales)
library(lwgeom)
library(googledrive)
# library(furrr)
# library(sfheaders)
library(units)
```

### Prep burned ft data
```{r}
### open data
burned_ft <- st_read("E:/usda_2023/usfs_fuel_treatments/western_us/all_burned_fuel_treats_year_burned_polygons.shp")

### get col names
colnam <- c("ft_id", "state", "activity_code", "activity", "treatment", "treatment_name",
            "date_comp", "day_comp", "month_comp", "year_comp",
            "first_fire_id", "first_fire_source", "fire_ig_date", "fire_id",
            "fire_year", "start_day", "end_day", "geometry")

### rename cols
colnames(burned_ft) <- colnam

### classify treatment types
rx_fuel_treat <- c("1111", "1112", "1113", "2540")
other_fire_fuel_treat <- "1130"
mech_fuel_treat <- c("1136", "1139", "1150", "1152", "1153", 
                     "1154", "1160", "1180", "2370", "4455")
rx_non_ft <- c("4471", "4491", "4541", "6101", "7050")
other_fire_non_ft <- "1102"
mech_non_ft <- c("1120", "2341", "2360", "2510", "2530", "4111", 
                 "4113", "4115", "4117", "4121", "4131", "4132", 
                 "4142", "4143", "4146", "4151", "4152", "4177", 
                 "4183", "4193", "4194", "4210", "4211", "4220", 
                 "4231", "4232", "4241", "4242", "4270", "4471", 
                 "4473", "4474", "4475", "4493", "4494", "4495", 
                 "4511", "4521", "4530", "4540", "6103", '6107', 
                 "7065", "7067", "9008", "9400")

### add column for overall treatment type
burned_ft <- burned_ft %>%
  mutate(overall_treat_type = ifelse(activity_code %in% mech_non_ft,
                                     "mech_non_ft",
                                     ifelse(activity_code %in% other_fire_non_ft,
                                            "other_fire_non_ft",
                                            ifelse(activity_code %in% rx_non_ft,
                                                   "rx_non_ft",
                                                   ifelse(activity_code %in% mech_fuel_treat,
                                                          "mech_fuel_treat",
                                                          ifelse(activity_code %in% other_fire_fuel_treat,
                                                                 "other_fire_fuel_treat",
                                                                 ifelse(activity_code %in% rx_fuel_treat,
                                                                        "rx_fuel_treat",
                                                                        "other")))))))

### remove Planned Treatment Burned in Wildfire, Wildfire - Human Ignition, and Wildfire - Natural Ignition 
burned_ft <- burned_ft %>%
  filter(!activity_code %in% c("1119", "4472", "1117", "1118"))

### treated for fuel vs not treated for fuel
burned_ft <- burned_ft %>%
  mutate(treat_for_fuel = ifelse(overall_treat_type %in% c("mech_fuel_treat",
                                                           "other_fire_fuel_treat",
                                                           "rx_fuel_treat",
                                                           "other_fire_non_ft"),
                                 "treat_for_fuel",
                                 "non_fuel_treat"))

### also make it numeric
burned_ft <- burned_ft %>%
  mutate(tff_num = ifelse(treat_for_fuel == "treat_for_fuel", 1, 0))
```

### unsuccessful code
### combine
Could I loop through fires and union polygons?
```{r}
### make vector of unique fires
fire_vector <- unique(burned_ft$first_fire_id)

### make output df
output_list <- list()

### loop
for (i in 1:length(fire_vector)) {
  
  ### get the first fire
  temp_fire <- fire_vector[i]
  
  ### subset burned_ft to that fire
  temp_fts <- burned_ft %>%
    filter(first_fire_id == temp_fire)
  
  # ### separate them
  # temp_fts <- temp_fts %>%
  #   st_cast("POLYGON")
  
  ### this gives me a list
  # ### combine
  # comb_fts <- temp_fts %>%
  #   st_union() #%>%
  #  # st_cast("POLYGON")
  
  # comb_fts <- do.call(rbind, comb_fts)
  
  ### intersect them
  # intersect_fts <- st_intersection(temp_fts)
  intersect_fts <- st_join(temp_fts, temp_fts, st_intersects)
  
  # ### drop non-intersections
  # intersect_fts <- intersect_fts %>%
  #   filter(n.overlaps > 1) %>%
  #   st_collection_extract()
    
    temp_fts %>%
    st_intersection() %>%
    ### don't want lines
    st_collection_extract()
  
  ### non-intersections
  non_intersect <- rmapshaper::ms_erase(temp_fts, intersect_fts)
  
}


ggplot() +
  geom_sf(data = temp_fts, aes(color = ft_id, fill = treat_for_fuel ), alpha = 0.2)

ggplot() +
  geom_sf(data = comb_fts)

ggplot() +
  geom_sf(data = intersect_fts, fill = "gray", alpha = 0.2) +
  geom_sf(data = intersect_fts_split, fill = "lightblue", alpha = 0.6)


```




### extract data to points for one fire
```{r}
### open fire pts
pts <- st_read("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/cbi_pts_mtbs.shp")

### filter to one fire
pts_1 <- pts %>%
  filter(fire_id == "ID4485611430720180802")

### subset burned_fts to fire
burned_fire <- burned_ft %>%
  filter(first_fire_id %in% pts_1$fire_id)

### intersect them
pts_ft <- st_intersection(pts_1, burned_fire)

### summarize
pts_ft_summ <- pts_ft
st_geometry(pts_ft_summ) <- NULL

# ### what does this look like?
# summ_n <- pts_ft_summ %>%
#   group_by(uid) %>%
#   summarise(n_occurrences = n())
# 
# ### merge
# pts_ft_summ <- merge(pts_ft_summ, summ_n, by = "uid")
# 
# ### look at the points that show up more than once
# pts_check <- pts_ft_summ %>%
#   filter(n_occurrences > 1)
# pts_check <- pts_ft_summ %>%
#   filter(uid %in% pts_check$uid)
# 
# ### are any of the fuel treatments after the fire?
# pts_check <- pts_check %>%
#   mutate(wrong_order = ifelse(date_comp > fire_ig_date, 1, 0))
# ### no, none are in the wrong order
# pts_check$wrong_order <- NULL

### add row number within each 
pts_ft_summ <- pts_ft_summ %>%
  group_by(uid) %>%
  mutate(rowid = row_number())

### simplify columns
pts_ft_summ <- pts_ft_summ %>%
  dplyr::select(uid, fire_id, rowid, ft_id, activity_code, activity,
                treatment, date_comp, first_fire_id, fire_ig_date,
                overall_treat_type, treat_for_fuel, tff_num)

### try making it wider?
pts_ft_summ <- pts_ft_summ %>%
  pivot_wider(names_from = rowid,
              values_from = c(ft_id,
                              activity_code,
                              activity,
                              treatment,
                              date_comp,
                              first_fire_id,
                              fire_ig_date,
                              overall_treat_type,
                              treat_for_fuel,
                              tff_num))

### this seems to work!
```

### extract data to points for sample fires
```{r}
### loop through fires to intersect

### make output object
pts_in_fts <- list()

### make vector of fires
unique_fires <- unique(pts$fire_id)

### loop
for (i in 1:length(unique_fires)) {
  
  ### get fire
  fire_i <- unique_fires[i]
  
  ### get pts
  pts_i <- pts %>%
    filter(fire_id %in% fire_i)
  
  ### get fts
  fts_i <- burned_ft %>%
    filter(first_fire_id %in% fire_i)
  
  ### intersect them
  pts_inter_i <- st_intersection(pts_i, fts_i)
  
  ### write to list
  pts_in_fts[[i]] <- pts_inter_i
  
}

### get out of list form
pts_df <- do.call(rbind, pts_in_fts)

rm(pts_in_fts)
gc()

# ### are any of the fuel treatments after the fire?
# pts_df_check <- pts_df %>% 
#   mutate(wrong = ifelse(date_comp > fire_ig_date, 1, 0)) %>% 
#   filter(wrong > 0)
### nope

### drop geometry
st_geometry(pts_df) <- NULL

### add row number within each 
pts_df <- pts_df %>%
  group_by(uid) %>%
  mutate(rowid = row_number())

### simplify columns
pts_df <- pts_df %>%
  dplyr::select(uid, fire_id, rowid, ft_id, activity_code, activity,
                treatment, date_comp, first_fire_id, fire_ig_date,
                overall_treat_type, treat_for_fuel, tff_num)

### try making it wider?
pts_df <- pts_df %>%
  pivot_wider(names_from = rowid,
              values_from = c(ft_id,
                              activity_code,
                              activity,
                              treatment,
                              date_comp,
                              first_fire_id,
                              fire_ig_date,
                              overall_treat_type,
                              treat_for_fuel,
                              tff_num))

### this seems to work!

### now need to add the pts that didn't intersect with any treatments back in

### make pts a normal df
st_geometry(pts) <- NULL

### merge
pts_all <- merge(x = pts,
                 y = pts_df,
                 by = c("uid", "fire_id"),
                 all = TRUE)

### write out
write_csv(pts_all,
          "E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_trial_fts.csv")
```

### determine which points should be dropped
Want to drop points that only received non-fuel treatments FTs, since these will not be appropriate control points
```{r}
### open pts
pts_all <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_trial_fts.csv")

### sum tff columns
pts_all <- pts_all %>%
  rowwise() %>%
  mutate(tff_all = sum(tff_num_1, tff_num_2, tff_num_3, tff_num_4,
                       tff_num_5, tff_num_6, tff_num_7,
                       na.rm = TRUE))

### classify
pts_all <- pts_all %>%
  mutate(category = ifelse(tff_all > 0, "treated",
                           ifelse((is.na(tff_num_1) & is.na(tff_num_2) & is.na(tff_num_3) 
                                   & is.na(tff_num_4) & is.na(tff_num_5) & is.na(tff_num_6) & is.na(tff_num_7)),
                                  "control", "drop")))

# check <- pts_all %>% dplyr::select(uid, tff_num_1:category)

### what's the breakdown?
table(pts_all$category)

# control    drop treated 
# 1709226   14027   46779 

### drop the drops
# pts_all <- pts_all %>%
#   filter(! category == "drop")

### simplify for csv
pts_all <- pts_all %>%
  dplyr::select(uid, category)

### write out
write_csv(pts_all,
          "E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_treat_control.csv")
```

### breakdown by fire
```{r}
### open pts
pts_all <- read_csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_trial_fts.csv") %>%
  dplyr::select(.,
                uid, fire_id)

### open treated pts
treat_control <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_treat_control.csv")

### merge
pts_all <- merge(pts_all,
                 treat_control,
                 by = "uid",
                 all.x = TRUE)

### summarize by fire
fire_summ <- pts_all %>%
  group_by(fire_id, category) %>%
  summarise(n_pts = n())
```


### simplify treated pts
```{r}
### open pts
pts_all <- read_csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_trial_fts.csv")

### open treated pts
treat_control <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_treat_control.csv") %>%
  filter(., category == "treated")

### filter pts_all to treated points
pts_all <- pts_all %>%
  filter(uid %in% treat_control$uid)

### clean up
rm(treat_control)
gc()

### what's the breakdown of the number of fuel treatments?
pts_all$n_na <- rowSums(is.na(pts_all))  
pts_all <- pts_all %>%
  mutate(n_ft = 7 - n_na/10)
table(pts_all$n_ft)
 #    1     2     3     4     5     6     7 
 # 8708  9567 23506  3392  1475   119    12

### see date range of treatments
pts_all <- pts_all %>%
  rowwise() %>%
  mutate(earliest_ft = min(date_comp_1, date_comp_2, date_comp_3, date_comp_4,
                           date_comp_5, date_comp_6, date_comp_7,
                           na.rm = TRUE),
         latest_ft = max(min(date_comp_1, date_comp_2, date_comp_3, date_comp_4,
                             date_comp_5, date_comp_6, date_comp_7,
                             na.rm = TRUE)),
         earliest_fire = min(fire_ig_date_1, fire_ig_date_2, fire_ig_date_3, fire_ig_date_4,
                             fire_ig_date_5, fire_ig_date_6, fire_ig_date_7,
                             na.rm = TRUE),
         latest_fire = max(min(fire_ig_date_1, fire_ig_date_2, fire_ig_date_3, fire_ig_date_4,
                               fire_ig_date_5, fire_ig_date_6, fire_ig_date_7,
                               na.rm = TRUE)))

# ### days between first and last treatment
# pts_all$days_btw_ft <- difftime(pts_all$earliest_ft,
#                                 pts_all$latest_ft,
#                                 units = c("days"))
# 
# ### what's the breakdown
# table(pts_all$same_date_ft)

# ### check it out
# pts_check <- pts_all %>%
#   dplyr::select(uid, earliest_fire, latest_fire,
#                 earliest_ft, latest_ft)

pts_check <- pts_all %>%
  dplyr::select(uid, fire_ig_date_1, fire_ig_date_2, fire_ig_date_3, fire_ig_date_4,
                fire_ig_date_5, fire_ig_date_6, fire_ig_date_7,
                date_comp_1, date_comp_2, date_comp_3, 
                date_comp_4, date_comp_5, date_comp_6, date_comp_7)

```

