---
title: "prelim_analysis"
output: html_document
date: "2024-02-09"
---

## Description
Initial analysis

Picks up after covariate_workflow.Rmd using subset of fires

Demo: https://bookdown.org/paul/applied-causal-analysis/lab-r-code-1.html


more fires:
WA4863311833720150814
CO3937110704320180703
CO3717510737520170802
CO3740210724320120513
NM3658710602220170516
AZ3448811140320160519
AZ3454211140020140708



## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load packages
library(tidyverse)
library(sf)
library(lubridate)
library(raster)
library(terra)
# library(viridis)
# library(scales)
library(lwgeom)
library(googledrive)
# library(furrr)
# library(sfheaders)
library(units)
library(rdrobust)
library(rddensity)
```

## Datasets
- cbi_pts_mtbs.shp: shp with location of points and composite burn index
- trial_pts_lcmap.csv: pre-fire land cover (need to drop points that were not forest pre-fire)
- trial_pts_dem.csv: elevation, slope, aspect (SRAI)
- trial_pts_tpi.csv: topographic position index
- trial_pts_treemap.csv: forest type
- pts_dist.csv: distance between points and boundaries
- pts_overlap_status.csv: whether or not each point overlaps with the boundary (need to drop pts that overlap with boundaries)
- allclimatedata.csv: monthly climate data from terraclimate and day-of fire weather from gridmet
- pts_treat_control.csv: whether each point is treated, control, or should be dropped (non-ft treatment)
- pts_within_fire_status.csv: whether each points' pixel is fully inside fire perimeter (so can drop pixels on very edge)

## Still need
- years since treatment
- simplified treatment type
- stand age
- how to summarize climate data

## Prelim combination
Output shp: E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/cbi_pts_nonclimate.shp
Column names: c("uid", "CBI_bc", "fire_id", "fire_year", "year_prior", "elevation", "slope", "aspect_srai", "tpi", "landcover", "lc_type", "forest_type", "forest_type_gen", "dist_bound", "overlap_bound", "category", "geometry", "dist_bound_tc")
```{r}
### open data layers

########################
### TOPOGRAPHY
########################
### open topography
dem <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/trial_pts_dem.csv")
tpi <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/trial_pts_tpi.csv")

### simplify
dem <- dem %>% 
  dplyr::select(uid, elevation, slope, aspect_srai)
tpi <- tpi %>% 
  dplyr::select(uid, tpi)

### combine
topog <- merge(x = dem,
               y = tpi,
               by = "uid")

### clean up
rm(dem, tpi)
gc()

########################
### LAND COVER
########################
### open land cover
lcmap <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/trial_pts_lcmap.csv")
treemap <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/trial_pts_treemap.csv")

### simplify
lcmap <- lcmap %>% 
  dplyr::select(uid, landcover, lc_type)
treemap <- treemap %>% 
  dplyr::select(uid, forest_type, forest_type_gen)

### combine
landcover <- merge(x = lcmap,
                   y = treemap,
                   by = "uid",
                   all.x = TRUE)

### clean up
rm(lcmap, treemap)
gc()

########################
### DIST TO BOUNDARIES
########################
### open layers
dist_bound <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_dist.csv")
overlap_status <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_overlap_status.csv")

### simplify
dist_bound <- dist_bound %>% 
  dplyr::select(uid, dist_bound)
overlap_status <- overlap_status %>% 
  dplyr::select(uid, overlap_bound)

### combine
rd_distance <- merge(x = dist_bound,
                     y = overlap_status,
                     by = "uid")

### clean up
rm(dist_bound, overlap_status)
gc()

########################
### TREATMENT STATUS
########################
treat_status <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_treat_control.csv")

########################
### LOCATED ENTIRELY WITHIN FIRE
########################
inside_fire <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/pts_within_fire_status.csv")

########################
### COMBINE THE ABOVE
########################
### topography and landcover
topo_lc <- merge(x = topog,
                 y = landcover,
                 by = "uid")
rm(topog, landcover)
gc()

### add in dist to boundaries
topo_lc_rd <- merge(x = topo_lc,
                    y = rd_distance,
                    by = "uid")
rm(topo_lc, rd_distance)
gc()

### add in treatment status
tlr_status <- merge(x = topo_lc_rd,
                    y = treat_status,
                    by = "uid")
rm(topo_lc_rd, treat_status)
gc()

### add in edge of fire status
tlr_status_inside <- merge(x = tlr_status,
                           y = inside_fire,
                           by = "uid")
rm(tlr_status, inside_fire)
gc()

########################
### PTS with SHP
########################
### open shp
pts <- st_read("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/cbi_pts_mtbs.shp")

### reorder cols
pts <- pts %>%
  dplyr::select(uid, CBI_bc, fire_id, fire_year, year_prior, geometry)

### merge in
pts_dat <- merge(x = pts,
                 y = tlr_status_inside,
                 by = "uid")

### update distance to border based on treatment/control
pts_dat <- pts_dat %>%
  mutate(dist_bound_tc = ifelse(category == "control",
                                dist_bound*(-1),
                                dist_bound))

### clean up
rm(tlr_status_inside, pts)
gc()
```
### Subset to valid points
Keep the following points: 
- lc_type == "treecover"
- category %in% c("treated", "control")
- overlap_bound == "nonoverlap"
```{r}
### subset pts
pts_dat_use <- pts_dat %>%
  filter(lc_type == "treecover") %>%  ## 316535 points are not forest
  filter(category %in% c("treated", "control")) %>% ## 14027 in "drop" category
  filter(overlap_bound == "nonoverlap") %>% ## 21474 overlapping boundaries
  filter(in_fire == "inside") ## 22999 points' pixels overlap the fire perimeter

### write out 
st_write(pts_dat_use,
         "E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/cbi_pts_nonclimate_use.shp")

### make csv
st_geometry(pts_dat_use) <- NULL

### write out
write_csv(pts_dat_use,
          "E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/cbi_pts_nonclimate_use.csv")
```

## Preliminary RDD
```{r}
### open data
pts_dat_use <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/cbi_pts_nonclimate_use.csv")

### summarize for each fire
table(pts_dat_use$fire_id, pts_dat_use$category)

### no valid points in CA3312011695319931027
```

### Try with the four fires together
```{r}
### subset
pts_use <- pts_dat_use %>%
  filter(!fire_id == "CA3312011695319931027")

### clean up
rm(pts_dat_use)
gc()

# ### fix colnames
# colnames(pts_use) <- c("uid", "CBI_bc", "fire_id", "fire_year", "year_prior", 
#                        "elevation", "slope", "aspect_srai", "tpi", "landcover", 
#                        "lc_type", "forest_type", "forest_type_gen", "dist_bound", 
#                        "overlap_bound", "category", "dist_bound_tc")
```

#### look at covariates
```{r}
### make sure category works
pts_use %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc,
                 y = category)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4)

### fire severity
pts_use %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc,
                 y = CBI_bc)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4) +
  xlab("Distance to the boundary (m)") +
  ylab("Composite burn index") +
  theme_bw() +
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 13)) +
  xlim(-500, 300) +
  NULL
ggsave("trial_fire_cbi_plot.png")

### elev
pts_use %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc,
                 y = elevation)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4) +
  xlab("Distance to the boundary (m)") +
  ylab("Elevation") +
  theme_bw() +
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 13)) +
  xlim(-500, 300) +
  NULL
ggsave("trial_fire_elev_plot.png")

### slope
pts_use %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc,
                 y = slope)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4) +
  xlab("Distance to the boundary (m)") +
  ylab("Slope") +
  theme_bw() +
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 13)) +
  xlim(-500, 300) +
  NULL
ggsave("trial_fire_slope_plot.png")

### aspect
pts_use %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc,
                 y = aspect_srai)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4) +
  xlab("Distance to the boundary (m)") +
  ylab("Aspect (SRAI)") +
  theme_bw() +
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 13)) +
  xlim(-500, 300) +
  NULL
ggsave("trial_fire_aspect_plot.png")

### tpi
pts_use %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc,
                 y = tpi)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4) +
  xlab("Distance to the boundary (m)") +
  ylab("Topographic position index") +
  theme_bw() +
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 13)) +
  xlim(-500, 300) +
  NULL
ggsave("trial_fire_aspect_plot.png")
```
#### plot with mean value per distance
```{r}
### round distance
pts_use_round <- pts_use %>%
  mutate(dist_bound_tc_r = round(dist_bound_tc, 0))

### summarize
pts_use_round <- pts_use_round %>%
  group_by(dist_bound_tc_r) %>%
  summarise(cbi = mean(CBI_bc),
            elev = mean(elevation),
            slope = mean(slope),
            aspect = mean(aspect_srai),
            tpi = mean(tpi))

### tpi
pts_use_round %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc_r,
                 y = tpi)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4) +
  xlab("Distance to the boundary (m)") +
  ylab("Topographic position index") +
  theme_bw() +
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 13)) +
  xlim(-500, 300) +
  NULL

### elevation
pts_use_round %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc_r,
                 y = elev)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4) +
  xlab("Distance to the boundary (m)") +
  ylab("Elevation (m)") +
  theme_bw() +
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 13)) +
  xlim(-500, 300) +
  NULL

### fire severity
pts_use_round %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc_r,
                 y = cbi)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4) +
  xlab("Distance to the boundary (m)") +
  ylab("Composite burn index") +
  theme_bw() +
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 13)) +
  xlim(-500, 300) +
  NULL

### slope
pts_use_round %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc_r,
                 y = slope)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4) +
  xlab("Distance to the boundary (m)") +
  ylab("Slope") +
  theme_bw() +
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 13)) +
  xlim(-500, 300) +
  ylim(0, 10) +
  NULL

### aspect
pts_use_round %>% 
  ggplot() +
  geom_point(aes(x = dist_bound_tc_r,
                 y = aspect)) +
  geom_vline(xintercept = 0, 
             color = "red", 
             linetype = 4) +
  xlab("Distance to the boundary (m)") +
  ylab("Aspect") +
  theme_bw() +
  theme(axis.text = element_text(size = 13),
        axis.title = element_text(size = 13)) +
  xlim(-500, 300) +
  NULL
```
#### rd density
```{r}
### check for elevation
summary(rdrobust(pts_use$elevation, pts_use$dist_bound_tc, all = TRUE))

### plots

### elevation
rdplot(pts_use$elevation, 
       pts_use$dist_bound_tc,
       x.lim = c(-700, 500),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Elevation (m)", 
       title = "")

### tpi
rdplot(pts_use$tpi, 
       pts_use$dist_bound_tc,
       x.lim = c(-700, 500),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Topographic position index", 
       title = "")

### aspect
rdplot(pts_use$aspect_srai, 
       pts_use$dist_bound_tc,
       x.lim = c(-700, 500),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Aspect (SRAI)", 
       title = "")

### slope
rdplot(pts_use$slope, 
       pts_use$dist_bound_tc,
       x.lim = c(-700, 500),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Slope", 
       title = "")
```

#### run rdrobust for covariates
```{r}
### elevation
summary(rdrobust(pts_use$elevation,
                 pts_use$dist_bound_tc,
                 all = TRUE))

### slope
summary(rdrobust(pts_use$slope,
                 pts_use$dist_bound_tc,
                 all = TRUE))

### aspect
summary(rdrobust(pts_use$aspect_srai,
                 pts_use$dist_bound_tc,
                 all = TRUE))

### tpi
summary(rdrobust(pts_use$tpi,
                 pts_use$dist_bound_tc,
                 all = TRUE))
```


#### try naive approach
```{r}
### use all defaults
rdd_test <- rdrobust(y = pts_use$CBI_bc,
                     x = pts_use$dist_bound_tc,
                     c = 0,
                     all = TRUE)
summary(rdd_test)

### plot it
rdplot(pts_use$CBI_bc, 
       pts_use$dist_bound_tc, 
       x.lim = c(-700, 500),
       x.label = "Distance to boundary (m)",
       y.label = "Composite burn index",
       title = "RDD estimate")

### check for placebo cutoff
summary(rdrobust(pts_use$CBI_bc,
                 pts_use$dist_bound_tc,
                 c = -100,
                 all = TRUE))

### add covariates
rdd_test <- rdrobust(y = pts_use$CBI_bc,
                     x = pts_use$dist_bound_tc,
                     covs = pts_use$elevation + pts_use$slope +
                       pts_use$aspect_srai + pts_use$tpi)
summary(rdd_test)
rdplot(pts_use$CBI_bc, 
       pts_use$dist_bound_tc, 
       covs = pts_use$elevation + pts_use$slope +
         pts_use$aspect_srai + pts_use$tpi,
       x.lim = c(-700, 500),
       x.label = "Distance to boundary (m)",
       y.label = "COmposite burn index",
       title = "RDD estimate")

### too big to plot
```

## Add in climate data
- allclimatedata.csv: monthly climate data from terraclimate and day-of fire weather from gridmet
```{r}
### open climate data
clim <- read.csv("E:/usda_2023/usfs_fuel_treatments/western_us/cbi_pts_trial/allclimatedata.csv")

### restrict to day of fire weather
fw <- clim %>%
  dplyr::select(uid, bi, erc, rmax, rmin, sph, tmmn, tmmx, vpd)

### convert units
fw <- fw %>%
  ### tmmn and tmmx are in kelvin --> celsius
  mutate(tmmn = tmmn - 273.15,
         tmmx = tmmx - 273.15)

### combine with the rest of the data
pts_use_fw <- merge(x = pts_use,
                    y = fw,
                    by = "uid",
                    all.x = TRUE)

### clean
rm(fw, pts_use)
gc()
```

#### run rdrobust for fire weather
```{r}
### burn index
rdplot(pts_use_fw$bi, 
       pts_use_fw$dist_bound_tc,
       x.lim = c(-700, 500),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Burn index", 
       title = "")

### energy release component
rdplot(pts_use_fw$erc, 
       pts_use_fw$dist_bound_tc,
       x.lim = c(-700, 500),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Energy release component", 
       title = "")

### rmax
rdplot(pts_use_fw$rmax, 
       pts_use_fw$dist_bound_tc,
       x.lim = c(-700, 500),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Maximum relative humidity", 
       title = "")

### rmin
rdplot(pts_use_fw$rmin, 
       pts_use_fw$dist_bound_tc,
       x.lim = c(-100, 100),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Minimum relative humidity", 
       title = "")

### sph
rdplot(pts_use_fw$sph, 
       pts_use_fw$dist_bound_tc,
       x.lim = c(-100, 100),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Specific humidity", 
       title = "")

### tmmn
rdplot(pts_use_fw$tmmn, 
       pts_use_fw$dist_bound_tc,
       x.lim = c(-100, 100),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Minimum temperature", 
       title = "")

### tmmx
rdplot(pts_use_fw$tmmx, 
       pts_use_fw$dist_bound_tc,
       x.lim = c(-100, 100),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Maximum temperature", 
       title = "")

### vpd
rdplot(pts_use_fw$vpd, 
       pts_use_fw$dist_bound_tc,
       x.lim = c(-100, 100),
       x.lab = "Distance to the boundary (m)",
       y.lab = "Vapor pressure deficit", 
       title = "")
```
#### rd test with fire weather
```{r}
### drop points with missing values
pts_use_fw <- pts_use_fw[complete.cases(pts_use_fw), ]

### check correlations

### make function
cor.prob <- function (X, dfr = nrow(X) - 2) {
  R <- cor(X, use="pairwise.complete.obs")
  above <- row(R) < col(R)
  r2 <- R[above]^2
  Fstat <- r2 * dfr/(1 - r2)
  R[above] <- 1 - pf(Fstat, 1, dfr)
  R[row(R) == col(R)] <- NA
  R
}
flattenSquareMatrix <- function(m) {
  if( (class(m) != "matrix") | (nrow(m) != ncol(m))) stop("Must be a square matrix.") 
  if(!identical(rownames(m), colnames(m))) stop("Row and column names must be equal.")
  ut <- upper.tri(m)
  data.frame(i = rownames(m)[row(m)[ut]],
             j = rownames(m)[col(m)[ut]],
             cor=t(m)[ut],
             p=m[ut])
}

### cor cols
corcols <- pts_use_fw[, c(6:9, 19:26)]

### check correlations
cor_table <- flattenSquareMatrix(cor.prob(corcols))
cor_table <- cor(pts_use_fw[, c(6:9, 19:26)])

### add covariates
summary(rdrobust(y = pts_use_fw$CBI_bc,
                 x = pts_use_fw$dist_bound_tc,
                 covs = pts_use_fw$elevation + pts_use_fw$slope +
                   pts_use_fw$aspect_srai + pts_use_fw$tpi +
                   pts_use_fw$bi + pts_use_fw$erc +
                   pts_use_fw$rmax + pts_use_fw$rmin +
                   pts_use_fw$sph + pts_use_fw$tmmn +
                   pts_use_fw$tmmx + pts_use_fw$vpd))
```

### glm with fire weather
```{r}
### open package
library(lme4)

### make treatment 0/1
pts_use_fw <- pts_use_fw %>%
  mutate(treat_stat = ifelse(category == "treated", 1, 0))

### convert factor columns
factor_cols <- c("uid", "treat_stat", "fire_id")
pts_use_fw <- pts_use_fw %>%
  mutate_each_(funs(factor(.)),
               factor_cols)

### convert elev to m
pts_use_fw <- pts_use_fw %>%
  mutate(elev_m = elevation/1000)

### run with random effect for fire
glm_fit <- glmer(CBI_bc ~ treat_stat + elev_m + slope + aspect_srai +
                   tpi + sph + vpd + (1|fire_id),
                 data = pts_use_fw)
model_summ <- summary(glm_fit)
model_coeff <- as.data.frame(model_summ$coefficients)

### run without random effect for fire
glm_fit_no_re <- glm(CBI_bc ~ treat_stat + elev_m + slope + aspect_srai +
                       tpi + sph + vpd,
                     data = pts_use_fw)
summary(glm_fit_no_re)
```



