---
title: "update_fuel_treat_cbi"
output: html_document
date: "2023-08-28"
---

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load packages
library(tidyverse)
library(sf)
library(lubridate)
library(raster)
library(terra)
```

## Perimeters
### Fuel treatments  

* Dataset: "Hazardous Fuel Treatment Reduction: Polygon"  
* Data downloaded 8/28/2023
* Data last updated Aug 18, 2023  
* url: https://data.fs.usda.gov/geodata/edw/datasets.php  
* metadata: https://data.fs.usda.gov/geodata/edw/edw_resources/meta/S_USA.Activity_HazFuelTrt_PL.xml  

```{r}
### Open fuel treatment database
ft <- st_read("E:/usda_2023/usfs_fuel_treatments/S_USA.Activity_HazFuelTrt_PL.shp") 

### Subset to states around CO
ft <- ft %>%
  filter(STATE_ABBR %in% c("UT", "CO",
                           "WY", "NE",
                           "KS", "OK",
                           "AZ", "NM"))

### Reproject fuel treatments
ft <- ft %>%
  st_transform(crs = 6350)

### Open Colorado boundary
co_bound <- raster::getData(name = "GADM",
                            country = 'USA',
                            level = 1) %>%
  st_as_sf() %>%
  filter(NAME_1 == "Colorado")

### Reproject CO
co_bound <- co_bound %>%
  st_transform(crs = 6350) %>%
  dplyr::select(NAME_1, geometry)

### Intersect treatment boundaries with CO
ft <- st_intersection(ft, co_bound)

### See which treatment types are present
unique(ft$METHOD)

### Filter out chemical and grazing
ft <- ft %>%
  filter(!METHOD %in% c("Animal",
                        "Chemical"))

### Take out treatments where completed date = NA
ft <- ft %>%
  drop_na(DATE_COMPL)

### Write out
st_write(ft,
         "E:/usda_2023/usfs_fuel_treatments/co_treatments.shp")
```

#### Look at specific treatments
```{r}
### how many different treatments are there?
ft_summ <- ft
st_geometry(ft_summ) <- NULL
ft_summ <- ft_summ %>%
  group_by(TREATMENT_, ACTIVITY) %>%
  summarise(n_rows = n())

### update TREATMENT_ column
ft <- ft %>%
  mutate(TREATMENT_ = ifelse(TREATMENT_ == "N/A",
                             "Wildfire",
                             ifelse(ACTIVITY == "Burning of Piled Material",
                                    "Machine Pile Burn",
                                    TREATMENT_)))

### still need to get rid of that stray NA!
ft$TREATMENT_[is.na(ft$TREATMENT_)] <- "Machine Pile Burn"

### Drop Grazing and Wildfire
ft <- ft %>%
  filter(!TREATMENT_ %in% c("Grazing", "Wildfire"))

### unique ID for fuel treatment footprints
tr_footprint <- ft %>%
  dplyr::select(SUID, ORG, ASU_NBR_UN, ASU_UOM,
                ADMIN_REGI, ADMIN_FORE, ADMIN_DIST,
                STATE_ABBR, OWNERSHIP_, PROC_REGIO,
                PROC_FORES, MGT_AREA_C, NBR_UNITS_,
                NBR_UNITS1, UOM, DATE_PLANN,
                DATE_AWARD, DATE_COMPL, FISCAL_YEA,
                FY_AWARDED, FISCAL_Y_1, FY_PLANNED,
                KEYPOINT, FUND_CODE, NEPA_DOC_N,
                ACCOMPLISH, ACCOMPLI_1) %>%
  distinct() %>%
  mutate(footprint_id = row_number())
st_geometry(tr_footprint) <- NULL

### merge back in
ft <- merge(x = ft, 
            y = tr_footprint,
            by = c("SUID", "ORG", "ASU_NBR_UN", "ASU_UOM",
                "ADMIN_REGI", "ADMIN_FORE", "ADMIN_DIST",
                "STATE_ABBR", "OWNERSHIP_", "PROC_REGIO",
                "PROC_FORES", "MGT_AREA_C", "NBR_UNITS_",
                "NBR_UNITS1", "UOM", "DATE_PLANN",
                "DATE_AWARD", "DATE_COMPL", "FISCAL_YEA",
                "FY_AWARDED", "FISCAL_Y_1", "FY_PLANNED",
                "KEYPOINT", "FUND_CODE", "NEPA_DOC_N",
                "ACCOMPLISH", "ACCOMPLI_1"),
            all.x = TRUE)

### make column that categorizes activities
ft <- ft %>%
  mutate(treat_cat = ifelse(TREATMENT_ %in% c("Biomass Removal", "Chipping", "Crushing", "Lop and Scatter", "Machine Pile", "Thinning"), "mechanical", ifelse(TREATMENT_ == "Broadcast Burn", "rx_fire", ifelse(TREATMENT_ == "Fire Use", "managed_wildfire", ifelse(TREATMENT_ %in% c("Machine Pile Burn", "Jackpot Burn"), "other", TREATMENT_)))))

### write out treatment key
ft_summ <- ft
st_geometry(ft_summ) <- NULL
ft_summ <- ft_summ %>%
  group_by(treat_cat, TREATMENT_, ACTIVITY) %>%
  summarise(n_rows = n())
ft_summ <- ft_summ %>%
  dplyr::select(-n_rows)
write_csv(ft_summ, "treatment_codes.csv")

#### List methods in each footprint
unique_methods <- ft 
st_geometry(unique_methods) <- NULL
unique_methods <-  unique_methods %>%
  group_by(footprint_id) %>%
  summarise(all_methods = list(unique(treat_cat)))

### write out ft
st_write(ft,
         "E:/usda_2023/usfs_fuel_treatments/co_treatments.shp")
```

### MTBS fire perimeters
```{r}
### open all fires
mtbs <- st_read("E:/fire_sev_rdd/mtbs/mtbs_perims_DD.shp") %>%
  st_transform(crs = 6350)

### get column for state
mtbs <- mtbs %>%
  mutate(state = stringr::str_extract(Event_ID, "^.{2}"))

### filter to CO and surrounding states
mtbs <- mtbs %>%
  filter(state %in% c("CO", "UT", "AZ", "NM", 
                      "WY", "OK", "KS", "NE"))

### reduce cols
mtbs <- mtbs %>%
  dplyr::select(Event_ID, Incid_Type, 
                Ig_Date, geometry)

### Write out
st_write(mtbs,
         "E:/usda_2023/mtbs_co.shp")
```

## How many rx treatments subsequently burned? (using only broadcast burns, in line with Anna's definition)
```{r}
### Open full treatment dataset
co_treat <- st_read("E:/usda_2023/usfs_fuel_treatments/co_treatments.shp") %>%
  st_transform(crs = 5070) 

### fix weird column names
co_treat <- co_treat %>%
  rename(tr_footprint = ftprnt_,
         treat_cat = tret_ct)

### restrict to rx fire
co_rx <- co_treat %>%
  filter(treat_cat == "rx_fire")

### Open MTBS 
mtbs <- st_read("E:/usda_2023/mtbs_co.shp") %>%
  st_transform(crs = 5070) %>%
  
  ### drop prescribed fires from this dataset
  filter(., Incid_Type %in% c("Unknown",
                              "Wildfire",
                              "Wildland Fire Use"))

### Separate out year as column
mtbs <- mtbs %>%
  mutate(date = day(Ig_Date),
         month = month(Ig_Date),
         year = year(Ig_Date))

### Add date cols for treatments
co_rx <- co_rx %>%
  mutate(date_comp = day(DATE_CO),
         month_comp = month(DATE_CO),
         year_comp = year(DATE_CO))

### treatments completed range from 1997-2023

### drop MTBS fires before 1997
mtbs <- mtbs %>%
  filter(year > 1996)

### drop treatments that were completed after end of MTBS time series
co_rx <- co_rx %>%
  filter(year_comp < 2021)

##########################################
##########################################
### are there footprints with multiple treatments in this dataset?
length(unique(co_rx$tr_footprint))
### 577 -- yes

#### figure out what's happening there
check <- co_rx
st_geometry(check) <- NULL
check <- check %>%
  group_by(tr_footprint) %>%
  summarise(all_methods = list(unique(ACTIVITY)))

#### which footprint has "Control of Understory Vegetation- Burning"?
ft_check <- co_rx %>%
  filter(ACTIVITY == "Control of Understory Vegetation- Burning")
### 3136
#### look at this footprint
ft_check <- co_rx %>%
  filter(tr_footprint == "3136")

### drop the row with "Control of Understory Vegetation- Burning" from the dataset
co_rx <- co_rx %>% 
  filter(!ACTIVITY == "Control of Understory Vegetation- Burning")
##########################################
##########################################

### Loop to figure out which treatments burned after treatment
store_intersect_all <- list()

for (i in 1:length(unique(co_rx$tr_footprint))) {
  
  ### progress bar
  print(paste0("STEP ", i))
  
  ### get treatment i
  co_tr_temp <- co_rx[i, ]
  
  ### subset to fires that burned after
  mtbs_temp <- mtbs %>%
    filter(Ig_Date > co_tr_temp$DATE_CO)
  
  ### Intersect
  temp_intersect <- st_intersection(co_tr_temp, mtbs_temp)
  
  ### store intersections as a list
  store_intersect_all[[i]] <- list(temp_intersect, unique(co_rx$tr_footprint)[i])
  
}

### Now need code to see how many treatments actually burned
### See how many treatments burned
co_treat_burn <- co_rx[1, ]
co_treat_burn <- co_treat_burn %>%
  mutate(tr_footprint = "empty")

### drop geom
st_geometry(co_treat_burn) <- NULL

### drop cols
co_treat_burn <- co_treat_burn %>%
  dplyr::select(tr_footprint)

### add cols for merge
co_treat_burn <- co_treat_burn %>%
  mutate(Event_ID = NA, 
         Incid_Type = NA, 
         Ig_Date = NA,
         date = NA, month = NA, year = NA)

for (i in 1:length(store_intersect_all)) {
# for (i in 1:10) { ## make sure it works on subset of data
  
  ### progress bar
  print(paste0("STEP ", i))
  
  ### make df
  temp_data <- as.data.frame(store_intersect_all[[i]][[1]])
  
  ### drop geom
  temp_data$geometry <- NULL
  
  ### Subset columns
  temp_data <- temp_data %>%
    dplyr::select(tr_footprint,
                  Event_ID, Incid_Type, 
                  Ig_Date,
                  date, month, year)
  
  if(nrow(temp_data) > 0) {
    
    ### rbind with co_treat_burn
    co_treat_burn <- rbind(co_treat_burn,
                           temp_data)
  } 
  
}

### drop the empty row
co_treat_burn <- co_treat_burn %>%
  filter(!tr_footprint == "empty")

### subset to wildfires
wild_treat <- co_treat_burn %>%
  filter(Incid_Type == "Wildfire")

### write this out
write_csv(wild_treat,
          "E:/usda_2023/co_treatments_that_burned.csv")

### Counts
length(unique(wild_treat$tr_footprint)) ## 47

### Look more closely
co_treat_burned <- co_rx %>%
  filter(tr_footprint %in% wild_treat$tr_footprint)

### write this out
st_write(co_treat_burned,
          "E:/usda_2023/co_treatments_that_burned.shp")
```

## Assign sample pts to treatment groups
### prep sample pts
```{r}
### open points
pts <- st_read("C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/all_sample_pts.shp") %>%
  st_transform(crs = 5070) %>%
  
  ### drop cols from previous analysis
  dplyr::select(-Evnt_ID,
                -Incd_Ty,
                -cb_svrt, 
                -brnd_mt)

### drop replicated cols
pts <- distinct(pts)

### fix weird column names
pts <- pts %>%
  rename(b1_Severit = b1_Svrt,
         b2_Severit = b2_Svrt,
         b3_Severit = b3_Svrt,
         b1_Sever_1 = b1_Sv_1,
         b2_Sever_2 = b2_Sv_1,
         b3_Sever_3 = b3_Sv_1,
         treated_1 = tretd_1,
         aspect_1 = aspct_1,
         rxburn_bin = rxbrn_b,
         aspect_co = aspct_c,
         slope_co = slope_c)
```

### rx fire?
```{r}
### intersect sample pts with rx fires (co_rx)
pts_rx <- pts %>%
  dplyr::select(uid, geometry) %>%
  st_intersection(co_rx)

### restrict cols
st_geometry(pts_rx) <- NULL
pts_rx <- pts_rx %>%
  dplyr::select(uid) %>%
  distinct() %>%
  mutate(treated_rx = 1)

### points outside of rx fire polygons
pts_non_rx <- pts %>%
  filter(!uid %in% pts_rx$uid) %>%
  mutate(treated_rx = 0)
st_geometry(pts_non_rx) <- NULL
pts_non_rx <- pts_non_rx %>%
  dplyr::select(uid, treated_rx)

### combine
pts_rx_01 <- rbind(pts_non_rx, 
                   pts_rx)
```

### burned in subsequent wildfires?
```{r}
### Which wildfires do we care about?
length(unique(wild_treat$Event_ID)) ## only 14 fires

### subset mtbs to those fires
mtbs_rx <- mtbs %>%
  filter(Event_ID %in% wild_treat$Event_ID)

### which sample points burned in these fires?
pts_mtbs <- pts %>%
  dplyr::select(uid, geometry) %>%
  st_intersection(mtbs_rx)

### restrict cols
st_geometry(pts_mtbs) <- NULL
pts_mtbs <- pts_mtbs %>%
  dplyr::select(uid) %>%
  distinct() %>%
  mutate(burned_wf = 1)

### points that did not burn in mtbs fires
pts_non_mtbs <- pts %>%
  filter(!uid %in% pts_mtbs$uid) %>%
  mutate(burned_wf = 0)
st_geometry(pts_non_mtbs) <- NULL
pts_non_mtbs <- pts_non_mtbs %>%
  dplyr::select(uid, burned_wf)

### combine
pts_mtbs_01 <- rbind(pts_non_mtbs, 
                     pts_mtbs)
```

### untreated points that burned in any wildfire?
```{r}
### subset points
untreat_burn_other <- pts %>%
  dplyr::select(uid, geometry) %>%
  filter(!(uid %in% pts_rx$uid |
             uid %in% pts_mtbs$uid)) 

### subset mtbs to those fires
mtbs_other <- mtbs %>%
  filter(!Event_ID %in% wild_treat$Event_ID)

### which sample points burned in these fires?
untreat_burn_other <- untreat_burn_other %>%
  st_intersection(mtbs_other)

### which fire ids are these?
other_fire_ids <- untreat_burn_other %>%
  dplyr::select(Event_ID, Incid_Type) 
st_geometry(other_fire_ids) <- NULL
other_fire_ids <- other_fire_ids %>%
  distinct()

### restrict cols
st_geometry(untreat_burn_other) <- NULL
untreat_burn_other <- untreat_burn_other %>%
  dplyr::select(uid) %>%
  distinct() %>%
  mutate(burned_other_wf = 1)

### points that did not burn in any fires
pts_never_burned <- pts %>%
  filter(!uid %in% untreat_burn_other$uid) %>%
  mutate(burned_other_wf = 0)
st_geometry(pts_never_burned) <- NULL
pts_never_burned <- pts_never_burned %>%
  dplyr::select(uid, burned_other_wf)

### combine
pts_other_fires <- rbind(untreat_burn_other, 
                     pts_never_burned)
```


### combine
```{r}
### combine rx and mtbs
pts_all <- merge(pts_rx_01,
                 pts_mtbs_01,
                 by = "uid")

### add columns to specify treatments
pts_all <- pts_all %>%
  mutate(treat_lvl = ifelse(treated_rx < 1 & burned_wf < 1,
                            
                            ### these points were NOT TREATED and did NOT BURN
                            "untreated_nowf",
                            
                            ### these points were NOT TREATED but DID BURN
                            ifelse(treated_rx < 1 & burned_wf > 0,
                                   "untreated_wf",
                                   
                                   ### TREATED and BURNED
                                   ifelse(treated_rx > 0 & burned_wf > 0,
                                          "treated_wf",
                                          
                                          ### otherwise, TREATED but did NOT BURN
                                          "treated_nowf"))))

# ### check that this looks right
# check <- pts_all %>% 
#   group_by(treated_rx, burned_wf, treat_lvl) %>% 
#   summarise(n_rows = n())

### summary stats
table(pts_all$treat_lvl)
#   treated_nowf     treated_wf untreated_nowf   untreated_wf 
#          2403            362         270297           6213 

### add wide version of the treatment level data
pts_all <- pts_all %>%
  mutate(treat_lvl_wide = treat_lvl) %>%
  pivot_wider(names_from = treat_lvl_wide,
              values_from = treat_lvl_wide) 

### update values in wide version
pts_all <- pts_all %>%
  mutate(untreated_nowf = ifelse(is.na(untreated_nowf), 0, 1),
         treated_nowf = ifelse(is.na(treated_nowf), 0, 1),
         untreated_wf = ifelse(is.na(untreated_wf), 0, 1),
         treated_wf = ifelse(is.na(treated_wf), 0, 1))

# ### verify unique labeling
# check <- pts_all %>%
#   mutate(test = untreated_nowf + treated_nowf + untreated_wf + treated_wf)

### add in column for whether the point burned in another wildfire
pts_all <- merge(pts_all,
                 pts_other_fires,
                 by = "uid")

### write this out
write_csv(pts_all,
          "pts_treatment_level.csv")
```

## CBI for pts that burned in comparison wf
### missing cbi for one fire
```{r}
# ### missing CBI for one fire: CO4060910587920200813
# 
# ### write out that fire perimeter for CBI in GEE
# missing_fire <- mtbs %>% filter(Event_ID == "CO4060910587920200813")
# ### assign julian start and end date based on state dates from Parks et al. 2019
# missing_fire <- missing_fire %>%
#   mutate(Start_Day = 152,
#          End_Day = 258)
# ### Select columns for GEE
# missing_fire <- missing_fire %>%
#   dplyr::select(Fire_ID = Event_ID,
#                 Fire_Year = year,
#                 Start_Day,
#                 End_Day,
#                 Incid_Type,
#                 geometry)
# ### Make sure date columns don't get read in with decimals
# missing_fire$Fire_Year <- as.character(missing_fire$Fire_Year, 0)
# missing_fire$Start_Day <- as.character(missing_fire$Start_Day, 0)
# missing_fire$End_Day <- as.character(missing_fire$End_Day, 0)
# ## Write out shp for gee
# st_write(missing_fire,
#          "C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/co_mtbs_missing_gee.shp")
```

### cbi for pts in sample fires
```{r}
### filter pts data
pts_cbi <- pts %>%
  filter(uid %in% pts_mtbs$uid) %>%
  dplyr::select(uid, geometry)

### we only need CBI from a handful of the fires I ran it for:
length(unique(mtbs_rx$Event_ID))

### list CBI files
cbi_list <- list.files(path = "C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/cbi_usda_gee",
                       pattern = "*\\.tif$",
                       full.names = TRUE)

### make column to match cbi file names
mtbs_rx <- mtbs_rx %>%
  mutate(cbi_files = paste0("C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/cbi_usda_gee/",
                            Event_ID, 
                            "_CBI_bc.tif"))

### subset cbi_list
cbi_subset <- subset(cbi_list, 
                     cbi_list %in% mtbs_rx$cbi_files)

### open files
cbi_rasts <- lapply(cbi_subset, terra::rast)

### combine rasters into SpatRasterCollection
cbi_src <- sprc(cbi_rasts)

### merge
cbi_merge <- merge(cbi_src)

### reproject
cbi_merge <- terra::project(cbi_merge,
                            "epsg:5070",
                            method = "bilinear")

# ### write out for visual check
# terra::writeRaster(cbi_merge,
#                    "C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/co_cbi_2.tif",
#                    filetype = "GTiff",
#                    overwrite = TRUE)
# st_write(sample_fires, "C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/co_sample_pts.shp")

### extract cbi to sample points
sample_cbi <- terra::extract(cbi_merge, 
                             pts_cbi,
                             bind = TRUE) %>%
  st_as_sf()

### why are there NA values?
# cbi_na <- pts_cbi %>%
#   filter(is.na(cbi_severity))
# cbi_na_burned <- st_intersection(cbi_na,
#                                  mtbs)
### these points are just barely outside the fire perimeter (difference between polygon of fire perimeter and raster...)

### add column to indicate whether point is within an mtbs perimeter
sample_cbi <- sample_cbi %>%
  mutate(outside_perimeter = ifelse(is.na(cbi_severity), 1, 0))

### get fire ID for these pts
pts_cbi <- st_intersection(sample_cbi, mtbs_rx)

### reduce columns
pts_cbi <- pts_cbi %>%
  dplyr::select(-cbi_files)
st_geometry(pts_cbi) <- NULL
```

### cbi for other fires
```{r}
### get relevant pts
cbi_other <- untreat_burn_other %>%
  mutate(cbi_files = paste0("C:/Users/kjsie/Documents/Dee Lab/USDA AFRI 2023/cbi_usda_gee/",
                            Event_ID, 
                            "_CBI_bc.tif"))

### subset cbi_list
cbi_subset_other <- subset(cbi_list, 
                     cbi_list %in% other_fire_ids$cbi_files)

### loop and extract
store_intersect_cbi <- list()

for (i in 1:length(cbi_subset_other)) {
  
  ### progress bar
  print(paste0("STEP ", i))
  
  ### fire name i
  fire_name_i <- cbi_subset_other[i]
  
  ### get pts that are in that fire
  fire_pts <- cbi_other %>%
    filter(cbi_files == fire_name_i)
  
  ### open corresponding cbi raster
  cbi_ras <- rast(fire_name_i)
  
  ### reproject
  cbi_ras <- terra::project(cbi_ras,
                            "epsg:5070",
                            method = "bilinear")
  
  ### extract cbi value
  cbi_ext <- terra::extract(cbi_ras, fire_pts,
                            bind = TRUE) %>%
    st_as_sf()
  
  
  ### drop geom
  st_geometry(cbi_ext) <- NULL
  
  if(nrow(cbi_ext) > 0) {
    
    ### store intersections as a list
  store_intersect_cbi[[i]] <- cbi_ext
  } 

}
  
### combine
cbi_other_severity <- bind_rows(store_intersect_cbi)  

### drop NA values
cbi_other_severity <- cbi_other_severity %>%
  filter(!is.na(CBI_bc))

### simplify
cbi_other_severity <- cbi_other_severity %>%
  dplyr::select(uid, 
                other_wf_id = Event_ID,
                Ig_Date,
                year,
                cbi_sev_other = CBI_bc)

### make code
cbi_other_severity <- cbi_other_severity %>%
  mutate(code = paste0(uid, "_", year))

### some of them burned multiple times
other_summ <- cbi_other_severity %>%
  group_by(uid) %>%
  summarise(max_year = max(year)) %>%
  mutate(code = paste0(uid, "_", max_year)) %>%
  dplyr::select(-max_year)

### multiple fires
mult_burn <- cbi_other_severity %>%
  filter(code %in% other_summ$code)

### drop those from cbi_other_severity
cbi_other_2 <- cbi_other_severity %>%
  filter(!uid %in% mult_burn$uid)

### combine
cbi_other_2 <- rbind(cbi_other_2,
                     mult_burn)
```

#### combine
```{r}
### check column names
names(pts_cbi)
names(cbi_other_2)

### update column names
pts_cbi <- pts_cbi %>%
  dplyr::select(uid, 
                cbi_sev = cbi_severity, 
                wf_id = Event_ID,
                wf_year = year)
cbi_other_2 <- cbi_other_2 %>%
  dplyr::select(uid,
                other_cbi_sev = cbi_sev_other,
                other_wf_id = other_wf_id,
                other_wf_year = year)

### merge them with pts_all
pts_all <- merge(x = pts_all,
                 y = pts_cbi,
                 by = "uid",
                 all = TRUE)
pts_all <- merge(x = pts_all,
                 y = cbi_other_2,
                 by = "uid",
                 all = TRUE)

### write this out
write_csv(pts_all,
          "pts_treatment_level_cbi.csv")

### combine with original sf df
all_data <- merge(pts,
                  pts_all,
                  by = "uid",
                  all = TRUE)
nrow(all_data)

### write out
st_write(all_data,
         "all_data_cbi.shp")

### write it out as a csv
write_csv(all_data,
         "all_data_cbi.csv")

```

#### output metadata
pts_treatment_level_cbi.csv  

* uid: unique identifier for the sample points  
* treated_rx: binary, 1 = treated with prescribed fire, 0 = no prescribed fire  
* burned_wf: binary, 1 = burned in subsequent wildfire that affected prescribed fire footprint, 0 = did not burn in subsequent wildfire that affected prescribed fire footprint  
* treat_lvl: combination of rx fire and wildfire exposure  
   - treated_wf: located inside prescribed fire perimeter AND burned in subsequent wildfire  
   - treated_nowf: located inside prescribed fire perimeter but did NOT burn in subsequent wildfire  
   - untreated_wf: located outside prescribed fire perimeter AND burned in subsequent wildfire (only including wildfires that intersect with rx fire treatment footprints)  
   - untreated_nowf: located outside prescribed fire perimeter and did NOT burn in subsequent wildfire (only including wildfires that intersect with rx fire treatment footprints)  
* untreated_nowf: binary, 1 = point received untreated_nowf treatment, 0 = point did not receive that treatment  
* treated_nowf: binary, 1 = point received treated_nowf treatment, 0 = point did not receive that treatment  
* untreated_wf: binary, 1 = point received untreated_wf treatment, 0 = point did not receive that treatment  
* treated_wf: binary, 1 = point received treated_wf treatment, 0 = point did not receive that treatment  
* burned_other_wf: binary, 1 = point was located outside of prescribed fire treatment footprint and did not burn in a wildfire that subsequently affected a prescrbed fire footprint, BUT it burned in a different wildfire  
* cbi_sev: composite burn index severity value for points that burned in wildfires that burned through prescribed fire footprints after prescribed fire treatment occurred (continuous value, 0-3. NA value indicates point was located outside of wildfire)  
* wf_id: MTBS Event_ID code for the wildfire that caused cbi_sev  
* other_cbi_sev: composite burn index severity value for points classified as burned_other_wf (points located outside of the prescribed fire footprints that burned in wildfires that did not affect the prescribed fire footprints) (continuous value, 0-3. NA value indicates point was located outside of wildfire)    
* other_wf_id: MTBS Event_ID code for the wildfire that caused other_cbi_sev  
* other_wf_year: year in which other_wf_id burned
